ZCB Pricing

### 2018-07-31 ZCB Pricing .Rmd
d

Antithetic_variates = function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r = 0.08,n=1000,s=100){
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path_inv= matrix(0,nrow = s+1, ncol = n)# matrix to generate interest paths using negative values of RV
  sim_path[1,] = r
  sim_path_inv[1,] = r
  z = rnorm(n) # Generate standard normal values
  z. = -z # Estimate negative value

@@

Moment_Matching=function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=100000,s=100){

@@

# We have decided to make use of the CIR model as our control variate process.
# Below is the closed form solution under the CIR model
bond_price_CIR <- function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=1,r0 = 0.08){
  h <- sqrt(alpha^(2)+2*sigma^(2))
  A <-(2*h*exp((alpha+h)*(T-t)/2)/(2*h+(alpha+h)*(exp((T-t)*(h))-1)))^((2*alpha*beta)/sigma^(2))
  B <-2*(exp((T-t)*(h))-1)/(2*h+(alpha+h)*(exp((T-t)*(h))-1))
  A*exp(-B*r0)
}

@@

CIR_MC= function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=1000,s=100){

  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r0

@@

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt)
  int=exp(-Sum)
  mean=mean(int)
  sd=sd(int)/sqrt(n)
  result=c(mean,sd)
  result

@@

Control_Variates_estimate= function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=1,r0 = 0.08,n=1000,s=100){
  Crude_Monte_Carlo(alpha,beta,sigma,T,r0,n,s)[1]- CIR_MC(alpha,beta,sigma,T,r0,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r0)
}

V=seq(0.01,0.05,0.01)
J=NULL
K=NULL
for ( i in 1:length(V)){
  J[i]=Control_Variates_estimate(r0=V[i])
  K[i]=bond_price(r=V[i])
}
P=(J-K)^2
P
```

>>>>

Antithetic_variates = function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=100000,s=200){
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path_inv= matrix(0,nrow = s+1, ncol = n)# matrix to generate interest paths using negative values of RV
  sim_path[1,] = r
  sim_path_inv[1,] = r
  z = rnorm(n) # Generate standard normal values
  z. = -z # Estimate negative value

@@

Moment_Matching=function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r0 = 0.08,n=100000,s=100){

@@

# We have decided to make use of the CIR model as our control variate process.
# Below is the closed form solution under the CIR model
bond_price_CIR <- function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=5,r = 0.08){
  h <- sqrt(alpha^(2)+2*sigma^(2))
  A <-(2*h*exp((alpha+h)*(T-t)/2)/(2*h+(alpha+h)*(exp((T-t)*(h))-1)))^((2*alpha*beta)/sigma^(2))
  B <-2*(exp((T-t)*(h))-1)/(2*h+(alpha+h)*(exp((T-t)*(h))-1))
  A*exp(-B*r)
}

@@

CIR_MC= function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=100000,s=200){

  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r

@@

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt)
  int=exp(-Sum)
  mean=mean(int)
  sd=sd(int)/sqrt(n)
  result=mean
  result

@@

Control_Variates_estimate= function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=5,r = 0.08,n=1000,s=100){
  Crude_Monte_Carlo(alpha,beta,sigma,T,r,n,s)[1]- CIR_MC(alpha,beta,sigma,T,r,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r)
}
